Outstanding Title

### 2017-04-26 writing/EpiDraft.Rmd
Add text to legionnaire's example

```{r}
#Power_calc momentarily out of commission :(
```

@@

Here is a plot of weekly counts of Legionnaire's disease in the United States from 2014 through 2016. This data was obtained from the CDC website.

@@

##Scraping the data

```{r, cache=TRUE}
library(rvest)
library(purrr)
library(dplyr)
library(stringr)
library(lubridate)
library(tidyr)
library(ggplot2)

@@

# Putting three years together

>>>>

```{r}
#Power_calc works except the casecrossover option
```

@@

We can perform power analyses on real data to determine whether we have a large enough sample size, relative risk, or average outcome value to provide sufficient power for testing hypotheses.  Presented here is weekly data from the CDC on mortality related to Legionnaire's disease (citation?). We focus on data from New York City, Pennsylvania, and the Midatlantic region from 2006 through 2017.

@@

```{r, echo=F, warning=F, message=F}
#Scraping the data from CDC

library(rvest)
library(purrr)
library(dplyr)
library(stringr)
library(lubridate)
library(tidyr)
library(ggplot2)

@@

# Putting all years together
